Nondeterministic Bigraphical Reactive Systems for Markov Decision Processes\thanks{Supported by organization x.}

### 2018-08-15 paper.tex
OKish state again

\begin{definition}[solid bigraph]
  A bigraph is \emph{solid} if these conditions hold:
  \begin{enumerate}
  \item no regions or outer names are idle (a region is called \emph{idle}
    if it is empty);
  \item no two sites or inner names are siblings;
  \item the parent of every site is a node;
  \item no outer name is linked to an inner name.
  \end{enumerate}
\end{definition}

% TODO: why we limit reaction rules to solid (stochastic bigraphs paper)
\begin{definition}[reaction rule] \label{reaction_rule}
  A \emph{reaction rule} is a pair
  \[ \mathsf{R} = (R : m \to J, R' : m \to J), \]
  sometimes written as $R \longrightarrowRHD R'$, where $R$ is the \emph{redex}
  and $R'$ the \emph{reactum}, and $R$ is solid. The rule generates all the
  \emph{ground reaction rules} $(r, r')$, where $r = (R \otimes \id_Y) \circ d$
  and $r' = (R' \otimes \id_Y) \circ d$ for some discrete ground
  \emph{parameter} $d : \epsilon \to \langle m, Y \rangle$. The \emph{reaction
    relation} $\longrightarrowrhd_{\mathsf{R}}$ over ground bigraphs is defined
  by
  \[ g \longrightarrowrhd_{\mathsf{R}} g' \text{ iff } g = D \circ r \text{ and
    } g' = D \circ r' \]
  for some bigraph $D$ and some ground reaction rule $(r, r')$ generated from
  $\mathsf{R}$.
\end{definition}

@@

%The next step towards...
% TODO: intro explaining how we are further generalising the extensions defined
% above

@@

>>>>

\begin{definition}[solid bigraph] \label{solid}
  A bigraph is \emph{solid} if these conditions hold:
  \begin{enumerate}
  \item no regions or outer names are idle (a region is called \emph{idle}
    if it is empty);
  \item no two sites or inner names are siblings;
  \item the parent of every site is a node;
  \item no outer name is linked to an inner name.
  \end{enumerate}
\end{definition}

\begin{definition}[reaction rule] \label{reaction_rule}
  A \emph{reaction rule} is a pair
  \[ \mathsf{R} = (R : m \to J, R' : m \to J), \]
  sometimes written as $R \longrightarrowRHD R'$, where $R$ is the \emph{redex}
  and $R'$ the \emph{reactum}, and $R$ is solid. The rule generates all the
  \emph{ground reaction rules} $(r, r')$, where $r = (R \otimes \id_Y) \circ d$
  and $r' = (R' \otimes \id_Y) \circ d$ for some discrete ground
  \emph{parameter} $d : \epsilon \to \langle m, Y \rangle$. The \emph{reaction
    relation} $\longrightarrowrhd_{\mathsf{R}}$ over ground bigraphs is defined
  by
  \[ g \longrightarrowrhd_{\mathsf{R}} g' \text{ iff } g = D \circ r \text{ and
    } g' = D \circ r' \]
  for some bigraph $D$ and some ground reaction rule $(r, r')$ generated from
  $\mathsf{R}$.
\end{definition}

The condition that $R$ must be solid ensures that the ground reaction rule is
unique for a given pair of $g$ and $D$.

@@

We extend PBRS even further by adding rewards to both reaction rules and
predicates, and grouping reaction rules into actions. This allows us to
represent any MDP as a nondeterministic BRS. This can be done either trivially
(see Example \ref{example}) or in a more efficient manner, by treating each
bigraph as a complex system, only parts of which are relevant to any given
reaction rule or predicate.

@@

Food for thought: what models have efficient (i.e. polynomial in size)
representation as BRSs? Can we define complexity classes (easy for everyone,
easy for bigraphs but not for everyone, hard for everyone)?
